---
title: "Margin Plot"
author: "Matt Brachmann, PhD Candidate, University of Guelph"
date: "Sept 21, 2018"
output: 
  html_document:
    theme: spacelab
    toc: TRUE
    toc_float: TRUE
---
### Library installation
1. Need to install libraries for the tidyverse, colouring, and to actually create
the plot

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(wesanderson)
library(ggExtra)
```



### Graphing with ggplot

Next we need to make a ggplot object. we will use the free iris data frame to make 
a scatterplot of Sepal length vs Petal length. 

```{r}

iris.graph = ggplot(data = iris, aes(x = Sepal.Length, y = Petal.Length))+
   geom_point(aes(col = Species))+
   geom_smooth(method = 'lm', se = FALSE, col = 'black')+
   labs(x = 'Sepal Length', y = 'Petal Length')+
   theme_bw()+
   scale_color_manual(values = wes_palette('Darjeeling1', n = 6, type ='continuous'))+
   theme(legend.position = 'none')
```

### Creating the marginal plot

Now we need to use the ggMarginal function from the ggextra package to 
actually add the histograms of the x and y variable distributions to the graph. 

```{r}
ggMarginal(iris.graph, margins = 'both', type = 'histogram', groupColour = T,
            groupFill = T, position = 'dodge', bins = 15)
```
